### 2018-12-11 writing/thesis/chapters/results.tex
Add preliminary table of convergence orders.

\chapter{Results}\label{chap:results}
\section{Convergence Test}
\newcommand{\error}{\operatorname{Total-Error}}
Before computing the error we first need to define the $L_p$ norms for a $p > 0$ by
% notation: https://en.wikipedia.org/wiki/Lp_space#Lp_spaces
\begin{equation}
  \label{eq:Lp-nrom}
  \Vert f(x) \Vert_p = \left( \int_K \vert f(x) \vert^p d\mu  \right)^{1/p}.
\end{equation}
We are interested in the total error which we define as the norm of the difference between an analytical solution $f(\bm{x}, t)$ and our approximation $\hat{f}(\bm{x}, t)$.
The error at a time $t$ is thus defined as
\begin{equation}
  \label{eq:error}
  \error(t,p) = \Vert f(\bm{x}, t) - \hat{f}(\bm{x}, t) \Vert_p.
\end{equation}

@@

\todo{Describe how to integrate the error for cells, and effect of volume}
% We are now ready to integrate the error for each cell.
% The output contains the position and conserved variables of each point.
% Each cell consists of $(N + 1)^d$ nodes, each associated with a quadrature weight $w_i$.
% The quadrature weights are associated with the reference cuboid.
% We thus need to map our element to the reference element, before we can compute the integral.

% Let $V$ denote the volume (or area) of each cell.
% For example, in two dimensions $V = \Delta x \, \Delta y$.
% The final result is then
% \begin{equation}
%   \Vert f_K(x) \Vert = \left( V \sum_{\bm{i}} \vert f(\bm{x}_{\bm{i}}) \vert^p w_{{\bm{i}}}  \right)^{1/p},
% \end{equation}
% where we used the mapping to the reference triangle (integration by substitution).

>>>>

\chapter{Results}\label{chap:results}
\section{Convergence Test}
\begin{table}[htb]
  \centering
\caption{Numerical order of convergence of ADER-DG method}%
\label{tab:convergence-order}
\begin{tabular}{@{}lS[table-format=1.2]S[table-format=1.2]S[table-format=1.2]@{}}
\toprule
{Order} & {L1} & {L2} & {LInf}\\ \midrule
1 & 2.03 & 2.00 & 1.92\\
2 & 2.56 & 2.55 & 2.56\\
3 & 3.44 & 3.41 & 3.42\\
4 & 4.27 & 4.27 & 4.33\\
5 & 5.36 & 5.32 & 5.26\\
6 & 5.38 & 5.35 & 5.17\\
\bottomrule
\end{tabular}
\end{table}
\newcommand{\error}{\operatorname{Total-Error}}

Before computing the error we first need to define the $L_p$ norms for a $p > 0$ by
% notation: https://en.wikipedia.org/wiki/Lp_space#Lp_spaces
\begin{equation}
  \label{eq:Lp-nrom}
  \Vert f(x) \Vert_p = \left( \int_K \vert f(x) \vert^p d\mu  \right)^{1/p}.
\end{equation}
We are interested in the total error which we define as the norm of the difference between an analytical solution $f(\bm{x}, t)$ and our approximation $\hat{f}(\bm{x}, t)$.
The error at a time $t$ is thus defined as
\begin{equation}
  \label{eq:error}
  \error(t,p) = \Vert f(\bm{x}, t) - \hat{f}(\bm{x}, t) \Vert_p.
\end{equation}

@@

\todo{Describe how to integrate the error for cells, and effect of volume}
We evaluate the cell-wise error with Gaussian quadrature.
 \begin{equation}
   \Vert f_K(x) \Vert_p = \left( V \sum_{\bm{i}} \vert f(\bm{x}_i, t) - \hat{f}(\bm{x}_i, t) \vert^p w_{{\bm{i}}}  \right)^{1/p},
 \end{equation}
where $V = \Delta x \Delta y$ is the volume of each two-dimensional cell.
The sum runs over all quadrature nodes $x_i$ with weights $w_i$.
We use ten nodes.
